Cradles of the first stars: self-shielding, halo masses, and multiplicity

### 2019-05-31 paper.tex
Rewording some of the conclusions

\begin{itemize}
	\item We find that Pop III stars are forming in halos with a mean mass of $7.7 \times 10^{5}$ M$_{\odot}$, which falls well below the M01 relation, until $\approx$ 380 Myr, at which point the mean halo mass rises above the M01 relation to a mean value of $3.7 \times 10^{6}$ M$_{\odot}$ due to the domination of LW radiation produced by metal-enriched stars in the most massive galaxy in the simulation box.
	\item Including \hh{} self-shielding results in a factor of up to 1.1 lower mass halos compared to M01, forming Pop III stars.
	\item There does not appear to be a strict correlation between LW intensity within a halo and the halo mass. LW intensity within a halo may not be as indicative of which halos may form Pop III stars as previously thought.
	\item Halos are likely to form multiple Pop III stars. At the instance of Pop III star formation, a halo will have formed a median number of four Pop III stars, up to a maximum of 16.
	\item By the end of the simulation, halos with masses > $10^{7} M_{\odot}$ acquire multiple Pop III stars due to mergers with smaller mass halos. This results in these high mass halos containing multiple Pop III stars, both young and old. 
\end{itemize}

@@

The assumptions often made about the formation of Pop III stars, like how they will only form in isolation and how \hh{} self-shielding will not affect formation, appear to break down when self-shielding is taken into account and restrictions about their formation are lifted. Further work needs to be done to determine why some halos form Pop III stars and others do not, to provide insight about the formation process of these stars and thus how they will affect their surrounding galactic environment. The effect of the LW intensity on host halo mass should be systematically investigated to determine whether or not this background radiation really has a profound effect on Pop III formation or not. These primordial objects need to be studied further to assist multi-messenger astronomers in finding these ancient systems.

>>>>

\begin{itemize}
	\item We find that Pop III stars are forming in halos with a mean mass of $7.7 \times 10^{5}$ M$_{\odot}$, which falls well below the M01 relation, until $\approx$ 380 Myr, at which point the mean halo mass rises above the M01 relation to a mean value of $3.7 \times 10^{6}$ M$_{\odot}$ due to the domination of LW radiation produced by metal-enriched stars in the most massive galaxy in the simulation box.
	\item \hh{} self-shielding allows halos below the M01 mass relation, as small as half as previously thought, to cool and form Pop III stars.  Self-shielding creates a disconnect between the LW intensity and the collapse, resulting in a broad mass distribution of metal-free star forming halos and no strict correlation between the two quantities.
	\item Halos are likely to form multiple Pop III stars. At the instance of Pop III star formation, a halo will have formed a median number of four Pop III stars, up to a maximum of 16.
	\item By the end of the simulation, halos with masses $>10^{7} M_{\odot}$ acquire multiple Pop III stars due to mergers with smaller mass halos, resulting galaxies with young and old metal-free stars. 
\end{itemize}

@@

The assumptions often made about the formation of Pop III stars, like how they will only form in isolation and how \hh{} self-shielding will not affect formation, appear to break down when self-shielding is taken into account and restrictions about their formation are lifted. Further work needs to be done to determine why some halos form Pop III stars and others do not, to provide insight about the formation process of these stars and thus how they will affect their surrounding pre-galactic environment. The effect of the LW intensity on host halo mass should be systematically investigated to determine whether or not this background radiation really has a profound effect on Pop III formation or not. Further constraints on these primordial objects will assist multi-messenger astronomers in identifying these ancient systems.
